---
title: "Department of Spanish and Portuguese"
subtitle: "Deptarment Meeting | Major updates"
author: "Joseph V. Casillas"
institute: "Rutgers University"
date: "2025-12-03 (Last update: `r Sys.Date()`)"
format: rutgers-revealjs
engine: knitr
---

```{r}
#| label: setup
#| include: false
library("tidyverse")
library("ggflowchart")
```

## Big picture - the problem {.center}


```{r}
med_credits <- median(
  c(33, 33, 30, 30, 33, 37, 27, 33, 30, 36, 36, 30, 33, 33, 30, 30, 36)
)
```

- Current major is out of date
- It does not help us confront current enrollment issues
- It does not reflect current practices at peer institutions nor at RU
  - Median credits for Spanish major in Big10 = `r med_credits`
  - At RU: **33** (French, Italian, Arabic), **36** (German, Korean, Chinese, Japanese), 


<!--
it is credit intensive, relative to other languages
we have bottlenecks in weird areas, interested students unable to take courses
-->

---

## Key questions: {.center}

1. How can we better serve students' needs
1. How can we get more majors?
1. Can we get more minors to become majors?

---

## Big picture - proposal {.center}

- Revamped learning goals
- Revamped major that better reflects learning goals and provides:
  - a simpler path to majoring in Spanish
  - more options for students whose primary interest may not be in Spanish

---

## Additional considerations: {.center}

We believe we need to...

- emphasize Spanish for the professions
- promote and utilize current strengths (e.g., TI program, heritage speakers of Spanish and Portuguese)
- further support upper-level enrollments

---

## Proposal {.center}

- 2 major options 
  - Spanish for Communities and Professions
  - Language intensive
- 33 credits each
- New 271 translation course

---

## Spanish for Communities and Professions {.smaller}

- This option is designed for students who wish to combine Spanish with another field of study or professional interest. 
- It is particularly appropriate for students interested in careers in health, education, environmental studies, public service, business, social sciences, international relations, or community-based work, as well as for students seeking to deepen their understanding of family or cultural heritage.
- Students in this option develop strong language skills while exploring how Spanish functions in diverse social, cultural, and professional contexts.

---

## Spanish for Communities and Professions {.smaller .scrollable}

::: {.fragment}
**A. Required Courses (4–6 courses [12-18 credits], depending on placement)**

- 201/203
- 202/204
- 215 Intro Hispanic Literature
- 261 Intro Study of Language
- 271 Intro to translation (new)
- 353 Spanish for community engagement
:::

::: {.fragment}
**B. Electives (5–7 [15-21 credits] courses, depending on placement)**  

- At least **three courses must be at the 300 level or above**
- Courses may be taught in Spanish, English, or Portuguese
:::

::: {.fragment}
Up to **6 credits** may be taken outside the department with approval from the Undergraduate Director. Examples of relevant fields include (but are not limited to): Latino and Caribbean Studies, Geography, Political Science, Comparative Literature, Cognitive Science, Computer Science, Linguistics, Environmental Studies, Public Health, Business, and related areas. Students are not limited to this list.
:::

---

## Language intensive

- The Language Intensive option is intended for students seeking advanced proficiency in Spanish and sustained engagement with literature, language, bilingualism/Second Language acquisition,
and translation. 
- This option is appropriate for students considering graduate study, teaching Spanish, translation and interpretation, or careers that require high levels of linguistic and cultural expertise

---

## Language intensive {.smaller .scrollable}

::: {.fragment}
**A. Required Lower-Division Courses (9 credits)**

- 215 Intro Hispanic Literature
- 261 Intro Study of Language
- 271 Intro to translation (new)

*Note*: Courses 201/203 and 202/204 may count toward the major as electives, allowing students to make progress toward the major early in their coursework.
:::

::: {.fragment}
**B. Upper Division Requirements: (12 credits)**

- A minimum of **12 credits at the 300 level or above**
:::

::: {.fragment}
**C. Electives (12 credits)**  

- Spanish courses from the 200–400 level
-  Up to 3 credits in Portuguese (810) may count toward the major
-  Up to 3 credits in courses taught in English (940) may count toward the major
:::

---

## Additional Notes for Both Options

- Major credit begins at the 200 level.
- Students are encouraged, but not required, to enroll in 400-level courses when available.
- Course sequencing is flexible.
- Students should meet regularly with a departmental advisor to plan a coherent and timely path through the major.

---

## {background-iframe="https://www.jvcasillas.com/upd/span_port_assessment/slides/new_major/33_credit_major.pdf" background-interactive=TRUE}

---

## 

[Timeline and next steps]{.emph .p-font style="font-size: 1.1em;"}

```{r}
library("ggplot2")
library("ganttrify")
library("dplyr")
library("tidyr")

# Gantt char of project timeline ----------------------------------------------

# Calculate difference in days from origin
time_diff <- function(date = "1982-11-03", format = "%Y-%m-%d", 
                      origin = "1970-01-01", units = "days") {
  start_date <- as.Date(origin, format)
  end_date   <- as.Date(date, format)
  out <- as.numeric(difftime(end_date, start_date, units = units))
  return(out)
}

# This is proof of concept, will change
time_line_df <- tribble(
 ~"wp",                ~"activity",                       ~"start_date",  ~"end_date", 
  "Preparation phase",  "Investigate peer institutions",   "2025-10-01",   "2025-10-22",
  "Preparation phase",  "Design major options",            "2025-10-22",   "2025-11-16",
  "Preparation phase",  "Meet w/ OUE",                     "2025-11-20",   "2025-12-01",
  "Preparation phase",  "Department approval",             "2026-01-23",   "2026-01-28",
  "Preparation phase",  "Design 271",                      "2026-01-17",   "2026-02-12",
  "Preparation phase",  "Submit proposals",                "2026-04-01",   "2026-04-14", 
  "Roll out phase",     "Launch 271",                      "2026-09-01",   "2026-12-17", 
  "Roll out phase",     "Launch new major options",        "2027-09-01",   "2027-12-17" 
)

# "Spots" can be used to mark when things actually occur on expected timeline
# Not used for now ("X" implies something is finished)
time_line_spots <- tribble(
  ~"activity",                 ~"spot_type",    ~"spot_date", 
   "Launch 271",                "Fall 2026",     "2026-10-15",
   "Launch new major options",  "Fall 2027",     "2027-10-15"
)

# Generate plot 
p_project_timeline <- ganttrify(
  project = time_line_df,
  spots = time_line_spots,
  by_date = TRUE,
  exact_date = TRUE,
  size_text_relative = 1,
  month_number = FALSE,
  font_family = "Times") + 
  geom_vline(xintercept = time_diff(date = Sys.Date()), lty = 3)

p_project_timeline
```

---

## Additional considerations {.center}

- "Ensure learning goals are lined up with curricular options"

- Discuss with other departments regarding credits outside dept (interdisciplinary option)

- Get feedback from current students about new options and current major

---

## Current major {background-color="black"}

"400 level - 6 credits, but not many options offered at 400 level in reality"

"Advanced grammar & comp: good in theory but when I took this class it just felt like a high school level grammar class - not as advanced. 
I thought it was really easy & I took it as a freshman."

"I think a grammar class would be good for the new intensive major - but idk if it makes sense now if you’re replacing it w/ the new translation course"

---

## Interdisciplinary major {background-color="black"}

"New major is cool I think it will attract more people into Spanish classes"

"Credit from other departments also cool - will attract more people to take the major. Why not add more depts? - psychology, international studies, etc."

"Nice breakdown between required and electives (credit wise)"

"Less required courses - depending on placement, good - will attract more people if they don’t want to start from scratch"

---

## Intensive major {background-color="black"}

"Capstone is a cool addition - what would that entail?"

"3 credits in 940 taught in English :( Makes sense to attract more students, but lowk goes against the intensive aspect. But since it’s only 3 credits makes sense"

"Nice breakdown between lower, upper, and electives (credit wise)"

"Credit from other departments also cool - will attract more people to take the major" 

---

## {.center}

::: {.columns}
::: {.column width="25%"}
:::

::: {.column width="50%"}
{{< qrcode https://forms.gle/DeMxrXfmKjz9FCYe7 id width=400 height=400 colorDark='#cc0033' >}}
:::

<!-- https://www.jvcasillas.com/upd/span_port_assessment/slides/new_major/33_credit_major.pdf -->
