---
title: "Department of Spanish and Portuguese"
subtitle: "Deptarment Meeting | Major updates"
author: "Joseph V. Casillas"
institute: "Rutgers University"
date: "2025-12-03 (Last update: `r Sys.Date()`)"
format: rutgers-revealjs
engine: knitr
---

```{r}
#| label: setup
#| include: false
library("tidyverse")
library("ggflowchart")
```

## Big picture - the problem {.center}


```{r}
med_credits <- median(
  c(33, 33, 30, 30, 33, 37, 27, 33, 30, 36, 36, 30, 33, 33, 30, 30, 36)
)
```

- Current major is out of date
- It does not help us confront current enrollment issues
- It does not reflect current practices at peer institutions nor at RU
  - Median credits for Spanish major in Big10 = `r med_credits`
  - At RU: **33** (French, Italian, Arabic), **36** (German, Korean, Chinese, Japanese), 


<!--
it is credit intensive, relative to other languages
we have bottlenecks in weird areas, interested students unable to take courses
-->

---

## Key questions: {.center}

1. How can we better serve students' needs
1. How can we get more majors?
1. Can we get more minors to become majors?

---

## Big picture - proposal {.center}

- Revamped learning goals
- Revamped major that better reflects learning goals and provides:
  - a simpler path to majoring in Spanish
  - more options for students whose primary interest may not be in Spanish

---

## Additional considerations: {.center}

We believe we need to...

- emphasize Spanish for the professions
- promote and utilize current strengths (e.g., TI program, heritage speakers of Spanish and Portuguese)
- further support upper-level enrollments

---

## Proposal {.center}

- 2 major options 
  - Interdisciplinary Spanish major
  - Language intensive Spanish major
- 33 credits each
- New 271 translation course
- 400-level capstone course

---

## Interdisciplinary option {.smaller}

- You want to learn Spanish and about Hispanic
cultures but you have another major
- You see yourself in a career that requires
cultural awareness and intercultural skills
- You are interested in contemporary issues that
impact Latinos in the US and international
relations with the Spanish-speaking worlds
- You want to communicate in Spanish in health
and business professions
- You want to understand your family heritage
- You want to add translation as a professional
skill

---

## Interdisciplinary option {.smaller .scrollable}

Consists of a minimum of 33 credits at the 200-
level or above completed with a grade of C or
better in each course.

::: {.fragment}
**I. 4-6 Required Spanish Language Courses depending on placement:**

- 201/203
- 202/204
- 215 Intro Hispanic Literature
- 261 Intro Study of Language
- 271 Intro to translation (new)
- 353 Spanish for community engagement
:::

::: {.fragment}
**II. 5-7 Electives depending on placement; 3 courses must be at the 300-level or above**  
Courses taught in Spanish, English, and
Portuguese accepted.
:::

::: {.fragment}
Up to 6 credits may be taken outside the
department: seek approval from department
Undergraduate Director for cognate courses from
other departments such as Cognitive Science,
Computer Science, English, Latino and Caribbean
Studies, and Linguistics.
:::

---

## Language intensive option

- You want everything listed in the interdisciplinary option and more…
- You want to speak Spanish fluently
- You see yourself teaching Spanish as a second language
- You have interest in a career in translation and interpreting
- You are passionate about languages
- You dream of living in a Spanish speaking country

---

## Language intensive option {.smaller .scrollable}

Consists of a minimum of 33 credits at the 200-level or above completed with a grade of C or better in each course.

::: {.fragment}
**I. Lower Division Requirements:**

- 200-level (6 credits)
- 215 Intro Hispanic Literature
- 261 Intro Study of Language
- 271 Intro to translation (new)
:::

::: {.fragment}
**II. Upper Division Requirements**
300 Level or above (2 of the 3 areas, 6 credits)

- Literature and culture (3 credits)
- Linguistics (3 credits)
- Translation (3 credits)
:::

::: {.fragment}
**III. Capstone (400-level, 3 credits)**
:::

::: {.fragment}
**IV. Electives (18 credits)**  
Choose Spanish courses from 201/203 through the
400-level  
Up to 3 credits can be taken in Portuguese (810)  
Up to 3 credits can be taken in 940 courses taught in English
:::

---

## Side by side {background-iframe="https://www.jvcasillas.com/upd/span_port_assessment/slides/new_major/33_credit_major.pdf" background-interactive=TRUE}

---

## 

[Timeline and next steps]{.pfont .emph}

```{r}
library("ggplot2")
library("ganttrify")
library("dplyr")
library("tidyr")

# Gantt char of project timeline ----------------------------------------------

# Calculate difference in days from origin
time_diff <- function(date = "1982-11-03", format = "%Y-%m-%d", 
                      origin = "1970-01-01", units = "days") {
  start_date <- as.Date(origin, format)
  end_date   <- as.Date(date, format)
  out <- as.numeric(difftime(end_date, start_date, units = units))
  return(out)
}

# This is proof of concept, will change
time_line_df <- tribble(
 ~"wp",                ~"activity",                       ~"start_date",  ~"end_date", 
  "Preparation phase",  "Investigate peer institutions",   "2025-10-01",   "2025-10-22",
  "Preparation phase",  "Design major options",            "2025-10-22",   "2025-11-16",
  "Preparation phase",  "Meet w/ Office of the Dean",      "2025-11-20",   "2025-12-01",
  "Preparation phase",  "Department approval",             "2026-01-17",   "2026-01-25",
  "Preparation phase",  "Design 271",                      "2026-01-17",   "2026-03-01",
  "Preparation phase",  "Submit proposal",                 "2026-04-01",   "2026-04-14", 
  "Roll out phase",     "Run 271",                         "2026-09-01",   "2026-12-17", 
  "Roll out phase",     "Open new major options",          "2027-09-01",   "2027-12-17" 
)

# "Spots" can be used to mark when things actually occur on expected timeline
# Not used for now ("X" implies something is finished)
time_line_spots <- tribble(
  ~"activity",          ~"spot_type",    ~"spot_date", 
   "HLS",                "deadline",      "2021-04-28", 
   "HLS",                "presentation",  "2021-10-07", 
   "CASPSLaP",           "deadline",      "2021-10-30", 
   "CASPSLaP",           "presentation",  "2022-02-19",
   "V1",                 "submit",        "2022-02-03", 
   "V2",                 "start",         "2022-10-01", 
   "V2",                 "submit",        "2022-11-11", 
   "V3",                 "start",         "2023-02-08", 
   "V3",                 "submit",        "2023-02-20", 
   "Typesetting",        "published",     "2023-08-23"
)

# Generate plot 
p_project_timeline <- ganttrify(
  project = time_line_df,
  #spots = time_line_spots,
  by_date = TRUE,
  exact_date = TRUE,
  size_text_relative = 1,
  month_number = FALSE,
  font_family = "Times") + 
  geom_vline(xintercept = time_diff(date = Sys.Date()), lty = 3)

p_project_timeline
```

---

## Additional considerations

---

## {.center}

::: {.columns}
::: {.column width="25%"}
:::

::: {.column width="50%"}
{{< qrcode https://forms.gle/DeMxrXfmKjz9FCYe7 id width=400 height=400 colorDark='#cc0033' >}}
:::

<!-- https://www.jvcasillas.com/upd/span_port_assessment/slides/new_major/33_credit_major.pdf -->
