---
title: "Department of Spanish and Portuguese"
subtitle: "Deptarment Meeting | AI survey"
author: "Joseph V. Casillas"
institute: "Rutgers University"
date: "2025-03-12 (Last update: `r Sys.Date()`)"
format: rutgers-revealjs
engine: knitr
execute: 
  fig-asp: 0.56
  out-width: "100%"
  fig-dpi: 300
  warning: false
  message: false
  cache: true
---

```{r}
#| label: setup
#| include: false
library("tidyverse")
library("here")
library("janitor")
library("brms")
library("ggdist")
library("lubridate")
library("ggimage")
library("glue")
library("emojifont")
```

```{r}
#| label: load-tidy
#| echo: false

temp <- read_csv(here("data", "spanport_ai_March 5, 2025_08.35.csv")) |>
  clean_names()

colnames <- slice(temp, 1) |> 
  pivot_longer(everything())

class_names <- tribble(
  ~"class", ~"label", 
  "1",  "span101", 
  "2",  "span102", 
  "3",  "span121", 
  "4",  "span131", 
  "5",  "span132", 
  "6",  "span160", 
  "7",  "span201", 
  "8",  "span202", 
  "9",  "span203", 
  "10",  "span204", 
  "11",  "span205", 
  "12",  "span206", 
  "13",  "span215", 
  "14",  "span225", 
  "15",  "span250", 
  "16",  "span261", 
  "17",  "span313", 
  "18",  "span325", 
  "19",  "span326", 
  "20",  "span331", 
  "21",  "span332", 
  "22",  "span333", 
  "23",  "span334", 
  "24",  "span335", 
  "25",  "span336", 
  "26",  "span342", 
  "27",  "span346", 
  "28",  "span348", 
  "29",  "span353", 
  "30",  "span360", 
  "31",  "span362", 
  "32",  "span363", 
  "33",  "span364", 
  "34",  "span366", 
  "35",  "span367", 
  "36",  "span368", 
  "37",  "span389", 
  "38",  "span390", 
  "39",  "span402", 
  "40",  "span403", 
  "41",  "span404", 
  "42",  "span405", 
  "43",  "span406", 
  "44",  "span419", 
  "45",  "span450", 
  "46",  "span462", 
  "47",  "span471", 
  "48",  "span477", 
  "49",  "span479", 
  "50",  "span488", 
  "51",  "span489", 
  "52",  "span490", 
  "53",  "span491", 
  "54",  "span492", 
  "55",  "span491", 
  "56",  "span491", 
  "57",  "span597", 
  "58",  "span493", 
  "59",  "span494", 
  "60",  "span499", 
  "61",  "span500", 
  "62",  "graduate", 
  "63",  "port101", 
  "64",  "port102", 
  "65",  "port130", 
  "66",  "port135", 
  "67",  "port160", 
  "68",  "port201", 
  "69",  "port203", 
  "70",  "port242", 
  "71",  "port493", 
  "72",  "port494", 
  "73",  "port497", 
  "74",  "port498", 
)

ai_types <- tribble(
  ~"val", ~"label", 
  1, "Electronic dictionaries",
  2, "Machine Translation Tools",
  3, "Chatbox - text (e.g., ChatGPT, copilot)",
  4, "Chatbox - spoken",
  5, "Language Learning Apps",
  6, "Social Media Apps",
  7, "Grammar Checking Tools (e.g., grammerly)",
  8, "Other",
)

ai_in_what_class <- tribble(
  ~"val", ~"label", 
  1, "100-level language classes", 
  2, "200-level language and culture classes", 
  3, "Linguistics classes", 
  4, "Literature classes", 
)

ai_goals <- tribble(
  ~"val", ~"label", 
  1, "Learn new vocabulary",
  2, "Learn new grammar",
  3, "Learn about a specific topic",
  4, "Practice conversation",
  5, "Help with reading difficult texts",
  6, "Create study materials",
  7, "Plan your learning",
  8, "To get answers when I’m not sure",
  9, "Other",
)

ai_how_used <- tribble(
  ~"val", ~"label", 
  1, "Look up words or expressions", 
  2, "Correct grammar", 
  3, "Ask questions about content", 
  4, "Ask questions about grammar", 
  5, "Learn about a specific content", 
  6, "Learn new words or expressions", 
  7, "Engage in a conversation in Spanish", 
  8, "Summarize a text", 
  9, "Translate a text", 
  10, "To complete an assignment when I didn’t have the time or resources", 
  11, "Other", 
)

dat <- temp |> 
  slice(-(1:2)) |> 
  select(
    response_id,
    start_date, 
    progress, 
    dur = duration_in_seconds, 
    class = q1, 
    class_2 = q20, 
    class_3 = q21, 
    ai_training = q2, 
    ai_training_info = q3, 
    ai_this_semester = q4, 
    ai_types = q5, 
    ai_specific = q6, 
    ai_in_what_class = q17, 
    ai_uses_in_class = q18, 
    ai_goals = q7, 
    ai_goals_info = q8, 
    ai_how_used = q9, 
    ai_how_info = q10, 
    ai_how_useful = q11_2, 
    ai_useful_info = q12, 
    ai_how_do_you_want_to_use = q13, 
    ai_dept_policy = q14
  ) |> 
  filter(response_id != "R_1o3OAxMPVdythsJ") |> 
  left_join(class_names, by = "class") |> 
  mutate(
    class = label, 
    class_2 = if_else(class_2 %in% class_names$class, label, NA), 
    class_3 = if_else(class_3 %in% class_names$class, label, NA), 
    ai_training = if_else(ai_training == "1", 1, 0), 
    ai_this_semester = if_else(ai_this_semester == "1", 0, 1), 
    ai_how_useful = (as.numeric(ai_how_useful) / 100) - 0.001, 
  ) |> 
  select(-label)
```


## Descriptives

```{r}
#| label: descriptives
n_participants <- nrow(dat)
total_enrollment <- 701
n_participants_prop <- n_participants / total_enrollment

avg_time <- dat |> 
  transmute(dur = as.numeric(dur)) |> 
  summarize(avg = mean(dur)) |>
  transmute(time = seconds_to_period(avg)) |> 
  pull() |> 
  round(digits = 1)

n_courses <- c(dat$class, dat$class_2, dat$class_3) |>
  na.omit() |> 
  unique() |> 
  length()
```

::: {.incremental}
- `r n_participants` participants 🧑🏽‍🎓
- `r round(n_participants_prop * 100, digits = 2)`% of total enrollment
:::

---

```{r}
#| label: fg-total-participation
#| fig-asp: 0.6
waffle_enrollment <- expand.grid(x = 1:30, y = 30:1) %>% 
  mutate(
    is_rep = c(rep("no", n_participants), rep("yes", 900 - n_participants)), 
    n = row_number(), 
    student = if_else(is_rep == "no", 
      here("slides", "ai", "index_files", "img", "student.png"), 
      here("slides", "ai", "index_files", "img", "student_grey.png")
    )
  )

waffle_enrollment |> 
  filter(n <= total_enrollment) |> 
  ggplot() + 
  aes(x, y, image = student) + 
  geom_image(size = 0.035) + 
  theme_void()
```

---

## Descriptives

- `r n_participants` participants 🧑🏽‍🎓
- `r round(n_participants_prop * 100, digits = 2)`% of total enrollment (`r total_enrollment` UG students)
- Enrolled in `r n_courses` distinct courses
- Completed survey in appox. `r round(avg_time)` minutes

---

## {.center}

```{r}
#| label: fg-participation
# Create top and bottom xlabs
part_labs <- tibble(
  x_bot = seq(0, 30, 5), 
  x_top = x_bot / n_participants
)

bind_rows(
    dat |> 
    select(class),
    dat |> 
    select(class = class_2), 
    dat |> 
    select(class = class_3)
  ) |> 
  group_by(class) |> 
  count() |> 
  ungroup() |> 
  na.omit() |> 
  mutate(
    prop = n / n_participants, 
    class = fct_reorder(class, prop, max)
  ) |> 
  ggplot() + 
  aes(x = n, y = class) + 
  geom_segment(
    aes(x = 0, xend = n), 
    linewidth = 3, color = "grey40"
  ) + 
  geom_point(size = 5, pch = 21, color = "white", fill = "#cc0033") + 
  scale_x_continuous(
    name = "N", 
    breaks = part_labs$x_bot, 
    sec.axis = sec_axis(name = "Proportion", ~ . / n_participants)
  ) + 
  labs(y = NULL) + 
  coord_cartesian(xlim = c(0, 20)) + 
  ds4ling::ds4ling_bw_theme(base_size = 16) + 
  NULL
```

---

## Have you received any training regarding the use of AI or other technologies for language learning? {.center}

---

## 

::: {.columns}
::: {.column}

<br>

```{r}
#| label: fg-ai-training
#| fig-asp: 1.0
#| fig-height: 4
#| fig-width: 4

n_training <- sum(dat$ai_training, na.rm = T)
perc_training <- round((n_training / n_participants) * 100)

waffle_ai_training <- expand.grid(x = 1:10, y = 10:1) %>% 
  mutate(
    is_rep = c(rep("no", n_training), rep("yes", 100 - n_training)), 
    n = row_number(), 
    student = if_else(is_rep == "no", 
      here("slides", "ai", "index_files", "img", "student.png"), 
      here("slides", "ai", "index_files", "img", "student_grey.png")
    )
  )

waffle_ai_training |> 
  filter(n <= n_participants) |> 
  ggplot() + 
  aes(x, y, image = student) + 
  geom_image(size = 0.1) + 
  theme_void()
```

:::

::: {.column}

<br><br><br>

<center>
[`r n_training` / `r n_participants`]{.emph .p-font style="font-size: 1.5em;"}  
(approx. `r perc_training`%)  
had [prior training]{.p-font style="font-size: 1.6em; color: #666666;"}  
with AI
</center>

:::
:::

---

## {.center}

```{r}
#| label: print-ai-training
#| results: "asis"
dat |> 
  filter(ai_training == 1) |> 
  mutate(
    ai_training_info = str_remove(ai_training_info, "\\(not on list\\) "), 
    print = glue('- "{ai_training_info}"')
  ) |> 
  pull(print)
```

---

## Have you used any technologies to do your assignments this semester? {.center}

---

## 

<br>

::: {.columns}
::: {.column}

```{r}
#| label: fg-ai-use
#| fig-asp: 1.0
#| fig-height: 4
#| fig-width: 4

n_use <- sum(dat$ai_this_semester, na.rm = T)
perc_use <- round((n_use / n_participants) * 100)

waffle_ai_use <- expand.grid(x = 1:10, y = 10:1) %>% 
  mutate(
    is_rep = c(rep("no", n_use), rep("yes", 100 - n_use)), 
    n = row_number(), 
    student = if_else(is_rep == "no", 
      here("slides", "ai", "index_files", "img", "student.png"), 
      here("slides", "ai", "index_files", "img", "student_grey.png")
    )
  )

waffle_ai_use |> 
  filter(n <= n_participants) |> 
  ggplot() + 
  aes(x, y, image = student) + 
  geom_image(size = 0.1) + 
  theme_void()
```
:::

::: {.column}

<br><br>

<center>
[`r n_use` / `r n_participants`]{.emph .p-font style="font-size: 1.5em;"}  
(approx. `r perc_use`%)  
used [technologies]{.p-font style="font-size: 1.6em; color: #666666;"}  
on an assignment
</center>

:::
:::

---

## What type of technologies have you used? {.center}

---

## {.center}

```{r}
#| label: fg-ai-types
types_labs <- tibble(
  x_bot = seq(0, 30, 5), 
  x_top = x_bot / 75
)

dat |> 
  select(ai_types) |> 
  na.omit() |> 
  transmute(to = str_split(ai_types, ",")) |> 
  unnest(cols = "to") |> 
  transmute(val = as.numeric(to)) |> 
  left_join(ai_types, by = "val") |> 
  group_by(label) |> 
  count() |> 
  ungroup() |> 
  mutate(
    possible = 8 * n_participants, 
    responses = sum(n), 
    prop_responses = n / responses, 
    prop_total = n / possible, 
    lab = case_when(
      label == "Electronic dictionaries" ~ "Electronic\ndictionaries", 
      label == "Machine Translation Tools" ~ "Machine translation\ntools", 
      label == "Chatbox - text (e.g., ChatGPT, copilot)" ~ "Chatbox - text\n(e.g., ChatGPT, copilot)", 
      label == "Chatbox - spoken" ~ "Chatbox - spoken", 
      label == "Language Learning Apps" ~ "Language learning apps", 
      label == "Social Media Apps" ~ "Social media apps", 
      label == "Grammar Checking Tools (e.g., grammerly)" ~ "Grammar checking tools\n(e.g., grammerly)", 
      label == "Other" ~ "Other"
    ), 
    lab = fct_reorder(lab, n, max) 
  ) |> 
  ggplot() + 
  aes(x = n, y = lab) + 
  geom_segment(
    aes(x = 0, xend = n), 
    linewidth = 3, color = "grey40"
  ) + 
  geom_point(size = 5, pch = 21, color = "white", fill = "#cc0033") + 
  scale_x_continuous(
    name = "N", 
    breaks = types_labs$x_bot, 
    sec.axis = sec_axis(name = "Proportion", ~ . / 75)
  ) + 
  coord_cartesian(xlim = c(0, 30)) + 
  labs(y = NULL) + 
  ds4ling::ds4ling_bw_theme(base_size = 16) + 
  theme(
    axis.text.y = element_text(hjust = 0.5), 
    axis.ticks.y = element_blank()
  )
```

---

## Specifically which technologies? {.center}

---

## {.center}

```{r}
#| label: fg-ai-specific-models

keepers <- c(
  "chatgpt", "spanishdict", "matecat", "linguee", "wordreference", 
  "word", "reference", "spanish", "dictionary", "grammarly", "deepl", 
  "google", "translate", "google translate", "chatgbt", "reverso", 
  "gemini", "copilot"
)

dat |> 
  select(ai_specific) |> 
  na.omit() |> 
  mutate(ai_specific = str_split(ai_specific, " ")) |> 
  unnest(col = "ai_specific") |> 
  mutate(
    ai_specific = str_remove(ai_specific, "\\."), 
    ai_specific = str_remove(ai_specific, ","), 
    ai_specific = str_to_lower(ai_specific)
  ) |> 
  filter(ai_specific %in% keepers) |> 
  mutate(
    ai_specific = case_when(
      ai_specific == "word" | ai_specific == "reference" ~ "wordreference", 
      ai_specific == "spanish" | ai_specific == "dictionary" ~ "spanishdict", 
      ai_specific == "chatgbt" ~ "chatgpt", 
      ai_specific == "google" | ai_specific == "translate" ~ "google translate", 
      TRUE ~ ai_specific
    )
  ) |> 
  group_by(ai_specific) |> 
  count() |> 
  ungroup() |> 
  transmute(
    n, 
    total_n = sum(n), 
    prop = n / total_n, 
    lab = fct_reorder(ai_specific, n, max)
  ) |> 
  ggplot() + 
  aes(x = prop, y = lab) + 
  geom_segment(
    aes(x = 0, xend = prop), 
    linewidth = 3, color = "grey40"
  ) + 
  geom_point(size = 5, pch = 21, color = "white", fill = "#cc0033") + 
  coord_cartesian(xlim = c(0, 0.3)) + 
  labs(x = "Proportion", y = NULL) + 
  ds4ling::ds4ling_bw_theme(base_size = 16) + 
  NULL
```

---

## In which classes did you use AI technologies? {.center}

---

## {.center}

```{r}
#| label: fg-ai-what-class

dat |> 
  select(ai_in_what_class) |> 
  na.omit() |> 
  transmute(val = as.numeric(ai_in_what_class)) |> 
  left_join(ai_in_what_class, by = "val") |> 
  group_by(label) |> 
  count() |> 
  ungroup() |> 
  transmute(
    lab = case_when(
      label == "100-level language classes" ~ "100-level\nlanguage classes", 
      label == "200-level language and culture classes" ~ "200-level\nlanguage/culture\nclasses", 
      label == "Linguistics classes" ~ "Linguistics\nclasses", 
      label == "Literature classes" ~ "Literature\nclasses"
    ), 
    n, 
    n_total = sum(n), 
    prop = n / n_total, 
    lab = fct_reorder(lab, prop, max)
  ) |> 
  ggplot() + 
  aes(x = prop, y = lab) + 
  geom_segment(
    aes(x = 0, xend = prop), 
    linewidth = 3, color = "grey40"
  ) + 
  geom_point(size = 5, pch = 21, color = "white", fill = "#cc0033") + 
  coord_cartesian(xlim = c(0, 0.5)) + 
  labs(x = "Proportion", y = NULL) + 
  ds4ling::ds4ling_bw_theme(base_size = 16) + 
  NULL
```

---

## How did your use of AI technologies differ for each class? {.center}

---

## {.scrollable}

```{r}
#| label: ai-uses-in-class-quotes
#| results: "asis"
dat |> 
  select(ai_uses_in_class) |> 
  na.omit() |> 
  filter(ai_uses_in_class != "N/A") |> 
  mutate(ai_uses_in_class = glue("- {ai_uses_in_class}")) |> 
  pull(ai_uses_in_class)
```

---

## {.smaller}

::: {.columns}
::: {.column}
### Themes and Definitions:

- **Efficiency**: Students used AI to complete tasks faster or reduce workload.
- **Subject-Specific Use**: AI was mainly used for translation and writing-related courses.
- **Idea Generation & Assistance**: Some students used AI to brainstorm or improve writing.
- **Minimal or No Use**: A few students avoided AI due to concerns over accuracy or reliance.
:::

::: {.column}
### Illustrative Quotes:

- "It makes things faster. This applies to professors as well."
- "I only used AI for translation courses, not for literature, linguistics, or writing."
- "I like to use AI to help me with my writing, whether it’s editing or generating ideas for main points."
- "I don’t really use too much AI because I don’t think it does things as well as a human."
:::
:::

---

## What were your goals in using these tools? {.center}

---

## {.center}

```{r}
#| label: fg-ai-goals

dat |> 
  select(ai_goals) |> 
  na.omit() |> 
  transmute(to = str_split(ai_goals, ",")) |> 
  unnest(cols = "to") |> 
  transmute(val = as.numeric(to)) |> 
  left_join(ai_goals, by = "val") |> 
  group_by(label) |> 
  count() |> 
  ungroup() |> 
  transmute(
    lab = case_when(
      label == "Create study materials" ~ "Create study\nmaterials", 
      label == "Help with reading difficult texts" ~ "Help reading\ndifficult texts", 
      label == "Learn about a specific topic" ~ "Learn about\nspecific topic", 
      label == "To get answers when I’m not sure" ~ "Get answers when\nI'm not sure", 
      label == "Learn new vocabulary" ~ "Learn new\nvocabulary", 
      label == "Learn new grammar" ~ "Learn new\ngrammar", 
      label == "Practice conversation" ~ "Practice\nconversation", 
      label == "Plan your learning" ~ "Plan my\nlearning", 
      TRUE ~ label
    ), 
    n, 
    total_n = sum(n), 
    prop = n / total_n, 
    lab = fct_reorder(lab, prop, max)
  ) |> 
  ggplot() + 
  aes(x = prop, y = lab) + 
  geom_segment(
    aes(x = 0, xend = prop), 
    linewidth = 3, color = "grey40"
  ) + 
  geom_point(size = 5, pch = 21, color = "white", fill = "#cc0033") + 
  coord_cartesian(xlim = c(0, 0.3)) + 
  labs(x = "Proportion", y = NULL) + 
  ds4ling::ds4ling_bw_theme(base_size = 16) 
```

---

## {.scrollable}

```{r}
#| label: ai-goals-info-quotes
#| results: "asis"
dat |> 
  select(ai_goals_info) |> 
  na.omit() |> 
  mutate(ai_goals_info = glue("- {ai_goals_info}")) |> 
  pull(ai_goals_info)
```

---

## {.smaller}

::: {.columns}
::: {.column}
### Themes and Definitions:

- **Efficiency & Productivity**: Using AI to complete work quickly or assist with last-minute tasks.
- **Translation & Comprehension**: AI used to translate words, confirm accuracy, and enhance understanding.
- **Grammar & Writing Assistance**: AI helped with sentence construction, proofreading, and grammar checks.
- **Speaking & Practice**: Some students used AI for conversational practice or understanding spoken language.
:::

::: {.column}
### Illustrative Quotes:

- "Get things done faster."
- "My goal was to look up words and outline ideas for presentations."
- "I use AI to proofread, correct mistakes, and improve my writing over time."
- "I needed a partner to practice Portuguese."

:::
:::

---

## How have you used these technologies? {.center}

---

## {.center}

```{r}
#| label: fg-ai-how-used

dat |> 
  select(ai_how_used) |> 
  na.omit() |> 
  transmute(to = str_split(ai_how_used, ",")) |> 
  unnest(cols = "to") |> 
  transmute(val = as.numeric(to)) |> 
  left_join(ai_how_used, by = "val") |> 
  group_by(label) |> 
  count() |> 
  ungroup() |> 
  transmute(
    lab = case_when(
      label == "Ask questions about content" ~ "Ask questions\nabout content", 
      label == "Ask questions about grammar" ~ "Ask questions\nabout grammar", 
      label == "Engage in a conversation in Spanish" ~ "Engage in\nconversation", 
      label == "Learn about a specific content" ~ "Learn about\nspecific content", 
      label == "Learn new words or expressions" ~ "Learn new\nwords/expressions", 
      label == "Look up words or expressions" ~ "Look up\nwords/expressions", 
      label == "Summarize a text" ~ "Summarize\ntext", 
      label == "To complete an assignment when I didn’t have the time or resources" ~ "Complete assignment\nwhen I didn't have\ntime/resources", 
      label == "Translate a text" ~ "Translate\ntext", 
      TRUE ~ label
    ), 
    n, 
    total_n = sum(n), 
    prop = n / total_n, 
    lab = fct_reorder(lab, prop, max)
  ) |> 
  ggplot() + 
  aes(x = prop, y = lab) + 
  geom_segment(
    aes(x = 0, xend = prop), 
    linewidth = 3, color = "grey40"
  ) + 
  geom_point(size = 5, pch = 21, color = "white", fill = "#cc0033") + 
  coord_cartesian(xlim = c(0, 0.3)) + 
  labs(x = "Proportion", y = NULL) + 
  ds4ling::ds4ling_bw_theme(base_size = 16) 
```

---

## {.scrollable}

```{r}
#| label: ai-how-info-quotes
#| results: "asis"
dat |> 
  select(ai_how_info) |> 
  na.omit() |> 
  mutate(ai_how_info = glue("- {ai_how_info}")) |> 
  pull(ai_how_info)
```

---

## {.smaller}

::: {.columns}
::: {.column}
### Themes and Definitions:

- **Checking & Learning**: Students used AI to check answers, verify grammar, and understand new vocab.
- **Writing & Proofreading**: AI assisted in structuring sentences and improving coherence.
- **Study Assistance**: AI acted as an on-demand tutor, creating study guides and simplifying concepts.
- **Limited Use**: Some students avoided AI due to concerns about reliance or inaccuracy.

:::

::: {.column}
### Illustrative Quotes:

- "I have used AI to learn unfamiliar vocab."
- "I ask AI how to format what I need to do."
- "I use AI to confirm verb conjugations and research small project details."
- "Sometimes I ask ChatGPT to dumb down concepts for better understanding."

:::
:::

---

## How useful or unuseful were these technologies? {.center}

---

## {.center}

```{r}
#| label: fg-ai-usefulness
#| echo: false

mod <- brm(
  formula = ai_how_useful ~ 1, 
  data = dat |> filter(!is.na(ai_how_useful)), 
  family = Beta(), 
  file = here("mods", "2025_ai_useful")
)

as_tibble(mod) |> 
  transmute(intercept = plogis(b_Intercept)) |> 
  ggplot() + 
  aes(x = intercept, y = 0) + 
  stat_halfeye(slab_fill = "#cc0033", pch = 21, point_fill = "white") + 
  geom_jitter(
    data = dat |> filter(!is.na(ai_how_useful)), 
    aes(x = ai_how_useful, y = -0.05), 
    pch = 21, color = "black", fill = "grey50", size = 4, alpha = 0.35, 
    height = 0.01, width = 0
  ) + 
  coord_cartesian(xlim = c(0, 1)) + 
  scale_x_continuous(
    breaks = seq(0, 1, 0.25), 
    labels = c("0.00\nNot useful", "0.25", "0.50", "0.75", "1.00\nVery useful")
  ) + 
  labs(x = NULL, y = NULL) + 
  ds4ling::ds4ling_bw_theme(base_size = 16) + 
  theme(
    axis.text.y = element_blank(), 
    axis.ticks.y = element_blank()
  )
```

---

## {.scrollable}

```{r}
#| label: ai-useful-info-quotes
#| results: "asis"

not_useful <- c(
  "same", "Very helpful", "n/a"
)

dat |> 
  select(ai_useful_info) |> 
  na.omit() |> 
  filter(!(ai_useful_info %in% not_useful)) |>
  mutate(ai_useful_info = glue("- {ai_useful_info}")) |> 
  pull(ai_useful_info)
```

---

## {.smaller}

::: {.columns}
::: {.column}
### Themes and Definitions:

- **Highly Useful**: AI was useful for translations, learning grammar, and checking work.
- **Needs Human Oversight**: AI was effective but required verification for accuracy.
- **Enhances Learning**: AI helped students recognize patterns and improve comprehension.
- **Limited Application**: Some AI tools worked better for certain tasks than others.

:::

::: {.column}
### Illustrative Quotes:

- "Without AI, I would struggle more with assignments."
- "AI helps confirm my conjugations and gives me confidence to learn."
- "I liked that AI explained concepts in different ways."
- "It is only useful if checked by a human, as it makes errors often."

:::
:::

---

## What would you like to be able to do with these tools?<br><br>What features are missing? {.center}

---

## {.scrollable}

```{r}
#| label: ai-how-do-you-want-to-use-quotes
#| results: "asis"
dat |> 
  select(ai_how_do_you_want_to_use) |> 
  na.omit() |> 
  filter(ai_how_do_you_want_to_use != "N/a") |> 
  mutate(ai_how_do_you_want_to_use = glue("- {ai_how_do_you_want_to_use}")) |> 
  pull(ai_how_do_you_want_to_use)
```

---

## {.smaller}

::: {.columns}
::: {.column}
### Themes and Definitions:

- **Speaking Practice**: Many students wanted AI tools that engage in spoken conversation.
- **Grammar & Writing Assistance**: Better recommendations for sentence structure and conjugation.
- **Flashcards & Study Materials**: Automated study aids like flashcards and practice problems.
- **Improved Accuracy**: AI tools should better recognize colloquial terms and refine responses.

:::

::: {.column}
### Illustrative Quotes:

- "I would like to engage in spoken conversations in Spanish to practice my skills."
- "I wish AI helped me with sentence structure and verb conjugation better."
- "It would be great if AI could generate flashcards without extra cost."
- "Some colloquial terms are missing in AI responses."

:::
:::

---

## Should the Department of Spanish and Portuguese have a strict policy regarding the use of AI?<br><br>What should this policy be? {.center}

---

## {.scrollable}

```{r}
#| label: ai-dept-policy-quotes
#| results: "asis"
dat |> 
  select(ai_dept_policy) |> 
  na.omit() |> 
  mutate(ai_dept_policy = glue("- {ai_dept_policy}")) |> 
  pull(ai_dept_policy)
```

---

## {.smaller}

::: {.columns}
::: {.column}
### Themes and Definitions:

- **Guided AI Use**: AI should be allowed for proofreading and study assistance but not for full assignments.
- **Strict Limitations**: Some students believe AI use should be minimized to encourage real learning.
- **Case-by-Case Approach**: AI should be regulated depending on the course and assignment type.
- **No Restrictions**: Others feel AI is a natural tool and should be freely available for learning.

:::

::: {.column}
### Illustrative Quotes:

- "AI should be used for proofreading, not for plagiarism."
- "AI should not be allowed for assignments that require demonstrated learning."
- "It should be used for checking work but not for full translations."
- "Students should be free to use AI as they see fit."

:::
:::

---

{{< qrcode www.jvcasillas.com/upd/span_port_assessment/slides/ai/index.html homepage width=400 height=400 colorDark='#cc0033' >}}
